---
title: STAT 444 FINAL PROJECT PROPOSAL
runtitle: 
author:
  - name: Angelo 
    surname: Carreon
    email: jaccarre@uwaterloo.ca
    label: e1, mark
    addressLabel: A
    sepNext: "," # use "," or \and; the last author not need this field
  - name: Hoseok
    surname: Lee
    email: h349lee@uwaterloo.ca
    label: e2, mark
    addressLabel: A
  - name: Joy
    surname: Chen
    email: z635chen@uwaterloo.ca
    label: e3, mark
    addressLabel: A
    sepNext: "and"
  - name: Steven
    surname: Shen
    email: s58shen@uwaterloo.ca
    label: e4, mark
    addressLabel: A
affiliation:
  - label: A
    name: Department of Statistics and Actuarial Science, University of Waterloo
    authorsLabels: e1,e2,e3,e4
abstract: |
  This paper contains our proposal for the STAT 444 final project. It outlines our dataset, performs some brief exploratory data analysis, then outlines our approach to fitting regression models to predict a final sale price of a house given its physical attributes. 
keyword-subclass: | 
 \begin{keyword}[class=MSC2020] % It must be define for aap, aop, aos journals. For aoas, sts is not used
 \kwd[Primary ]{00X00}
 \kwd{00X00}
 \kwd[; secondary ]{00X00}
 \end{keyword}
keywords:
  - housing
  - advanced regression
predefined-theoremstyle: true # use in section Environments for Axiom, Theorem, etc
bibliography: ims.bib
biblio-style: imsart-nameyear # alternative: imsart-number
output:
  rticles::ims_article:
    journal: aoas # aap, aoas, aop, aos, sts. See documentation
    toc: false # Please use for articles with 50 pages and more
header-includes:
- \usepackage{listings}
- \usepackage{xcolor}
- \usepackage{float}
- \floatplacement{figure}{H}
editor_options: 
  markdown: 
    wrap: 80
---

```{r setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(knitr)
library(readr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(gridExtra)

opts_chunk$set(tidy.opts=list(width.cutoff=75))
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

\newenvironment{kframe}{}{}

# Introduction to our chosen dataset 
Our project aims to assess the feasibility of utilizing regression techniques for interpolating and modeling housing prices. We have selected a dataset of housing prices in Ames, Iowa, along with their features from the *Journal of Statistics Education* [@cock2011amesdataset]. This dataset was prepared by Dean De Cock for use as an end-of-semester regression project. His intent was to provide data of substantial size ($n=2930$) with easy-to-understand variables that are known to affect the final sale price such as build date, lot size, and living space square footage. Applying this to today's real estate market, we wish to answer the following question: *which regression method best predicts the prices of houses given their characteristics*?

# Exploratory Data Analysis

This dataset contains 2930 rows and 82 columns. There are 80 explanatory variables, consisting of 23 nominal, 23 ordinal, 14 discrete, and 20 continuous variables. Several columns contain many missing values and will be dropped before we begin fitting models. As highlighted in De Cock's paper, several unusual outlier house sales exist in the data; these will also be removed. There are no duplicate rows.

As seen in table \ref{resp}, the distribution of `Sale Price` is significantly right-skewed. The sale prices range from \$12,789 to \$755,000 with a mean of \$180,796 and a standard deviation of \$79,886.69. To achieve a more normal distribution, we can apply a log transformation on the dependent variable, as seen below:

```{r, echo=FALSE, results=FALSE, message=FALSE}
housing <- read_csv("house-prices-advanced-regression-techniques/train.csv")
nrow(housing)
ncol(housing)

# remove column Order since it's just row index
housing <- housing[ , !(names(housing) == "Order")]
```

```{r, echo=FALSE, results=FALSE, message=FALSE}
# Alley: Type of alley access to property
sum(!is.na(housing$Alley))      # only 198 observations
# Pool.QC: Pool quality
sum(!is.na(housing$Pool.QC))    # only 13 observations
# Misc.Feature: Miscellaneous feature not covered in other categories
sum(!is.na(housing$Misc.Feature)) # only 106 observations
# Fence: Fence quality
sum(!is.na(housing$Fence))  # only 572 observations
# Fireplace.Qu: Fireplace quality
sum(!is.na(housing$Fireplace.Qu)) # only 1508 observations

# remove column alley, pool QC, Misc Feature
drops <- c("Alley","Pool.QC", "Fence", "Misc.Feature")
newHousing <- housing[ , !(names(housing) %in% drops)]

# Check for duplicates in the entire dataset (0 duplicates)
duplicates <- housing[duplicated(housing), ]
dim(duplicates)
```

```{r, echo=FALSE, fig.height=3, fig.width=8, fig.cap="Histograms of the response variable, Sale Price\\label{resp}"}
par(mfrow=c(1,2), mai=c(1, 1, 1, 1))
options(scipen=10)
hist(housing$SalePrice, xlab = "Property Sale Price", main = "Histogram of Sale Price")
lines(housing$SalePrice, col = 4, lwd = 2)
par(new=TRUE)   
plot(density(housing$SalePrice), col=2, lwd = 2, yaxt="n", xaxt="n",
     bty='n', xlab="", ylab="", main='')
lines(density(log(housing$SalePrice)), col="blue")
axis(4, las=1)

hist(log(housing$SalePrice), xlab = "log(Sale Price)", main = "Histogram of log(Sale Price)", breaks = 20)
par(new=TRUE)   
plot(density(log(housing$SalePrice)), col=2, lwd = 2, yaxt="n", xaxt="n",
     bty='n', xlab="", ylab="", main='')
axis(4, las=1)
```

Some variables of interest are `Neighbourhood` and `LotArea`, where we see in table \ref{neighbourhood} to have significant differences in the average property sale price. One way in which these neighborhoods could differ is in the size of the lots of the houses that reside there. Our team would need to consider variable associations such as these to deal with collinearity.

```{r, echo=FALSE, fig.height=2, fig.width=8, fig.cap="Plots showing the distribution of final Sale Price across the different Neighborhoods\\label{neighbourhood}"}

subset_housing = housing[housing$LotArea < 50000,]

plot1 = ggplot(
  subset_housing, 
  aes(x=reorder(Neighborhood, SalePrice, FUN=median),y=SalePrice)
) + 
  geom_boxplot(
    color="black", 
    fill="yellow"
  ) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  xlab("Neighbourhood") + 
  ylab("Sale Price ($)") +
  ylim(0, 400000)

plot2 = qplot(
  x = LotArea,
  y = SalePrice,
  data = subset_housing,
  color = Neighborhood,
  show.legend = FALSE
) +
  xlab("Lot Area, coloured by neighbourhood") + 
  ylab("Sale Price ($)") +
  xlim(0, 20000) +
  ylim(0, 500000)

grid.arrange(plot1, plot2, ncol=2)
```

# Plan 
The objective of this study is to determine the
viability and effectiveness of employing additive models, splines, and
polynomial regression for predicting house prices. We focus our attention on the following:

\begin{itemize}
\item
  \textbf{Accuracy}: Assess the predictive accuracy of additive models,
  splines, and polynomial regression in comparison to traditional
  regression models commonly used in the real estate domain.
    \vspace{0.2cm}
\item
  \textbf{Flexibility}: Analyze the ability of these techniques to
  capture complex relationships between house price predictors, such as
  square footage, location, number of bedrooms, and other relevant
  features.
  \vspace{0.2cm}
\item
  \textbf{Interpretability}: Evaluate the interpretability and
  explainability of the models, ensuring that the predictions can be
  easily understood and justified by stakeholders.
  \vspace{0.2cm}
\end{itemize}
To achieve our objective, we propose the following methodology as an
outline:

\begin{enumerate}
\item
  \textbf{Initial Benchmark}: Use the performance of linear regression, with simple categorical encoding, on the full
  feature set as an initial benchmark.
  \vspace{0.2cm}
\item
  \textbf{Data Preprocessing}: Handle missing/invalid values and outliers and perform feature engineering to enhance
  the models' predictions. To mitigate the "curse of dimensionality" and reduce collinearity in the dataset, we
   will use a low variance filter and clustering techniques such as Principal Component Analysis (PCA).
   \vspace{0.2cm}
\item
  \textbf{Model Implementation}: Develop additive models, splines, and
  polynomial regression models using appropriate algorithms and
  frameworks, such as generalized additive models (GAMs) and polynomial
  regression libraries in R. We will also apply penalization techniques
  to prevent overfitting (e.g. forward/backward selection, LASSO/Ridge regression)
  while including interactions between covariates to model any non-linear relationships.
  \vspace{0.2cm}
\item
  \textbf{Model Evaluation}: Assess the performance of the models using
  appropriate evaluation metrics, such as mean squared error (MSE), root
  mean squared error (RMSE), and R-squared values and compare the
  results with benchmark models.
  \vspace{0.2cm}
\item
  \textbf{Interpretation and Explainability}: Examine the contributions of each
  feature and the underlying relationships identified by the models. Visualize the results in an intuitive yet
  comprehensive manner.
\end{enumerate}

<!-- \newpage -->
<!-- \newpage -->
<!-- # Introduction -->
<!-- This template helps you to create a properly formatted \LaTeXe\ manuscript. -->
<!-- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
<!-- %% `\ ' is used here because TeX ignores    %% -->
<!-- %% spaces after text commands.              %% -->
<!-- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
<!-- Prepare your paper in the same style as used in this sample .pdf file. -->
<!-- Try to avoid excessive use of italics and bold face. -->
<!-- Please do not use any \LaTeXe\ or \TeX\ commands that affect the layout -->
<!-- or formatting of your document (i.e., commands like \verb|\textheight|, -->
<!-- \verb|\textwidth|, etc.). -->

<!-- # Section headings -->

<!-- Here are some sub-sections: -->

<!-- ## A sub-section -->

<!-- Regular text. -->

<!-- ### A sub-sub-section -->

<!-- Regular text. -->

<!-- # Text -->

<!-- ## Lists -->

<!-- The following is an example of an *itemized* list, two levels deep. -->

<!-- * This is the first item of an itemized list.  Each item -->
<!--   in the list is marked with a "tick." The document -->
<!--   style determines what kind of tick mark is used. -->
<!-- * This is the second item of the list.  It contains another -->
<!--   list nested inside it. -->
<!--   - This is the first item of an itemized list that -->
<!--     is nested within the itemized list. -->
<!--   - This is the second item of the inner list.  \LaTeX\ -->
<!--     allows you to nest lists deeper than you really should. -->
<!-- - This is the third item of the list. -->

<!-- The following is an example of an *enumerated* list of one level. -->

<!-- \begin{longlist} -->
<!-- \item This is the first item of an enumerated list. -->
<!-- \item This is the second item of an enumerated list. -->
<!-- \end{longlist} -->

<!-- The following is an example of an *enumerated* list, two levels deep. -->
<!-- \begin{longlist} -->
<!-- \item[1.] -->
<!-- This is the first item of an enumerated list.  Each item -->
<!-- in the list is marked with a ``tick.''.  The document -->
<!-- style determines what kind of tick mark is used. -->
<!-- \item[2.] -->
<!-- This is the second item of the list.  It contains another -->
<!-- list nested inside of it. -->
<!-- \begin{longlist} -->
<!-- \item -->
<!-- This is the first item of an enumerated list that -->
<!-- is nested within.   -->
<!-- \item -->
<!-- This is the second item of the inner list.  \LaTeX\ -->
<!-- allows you to nest lists deeper than you really should. -->
<!-- \end{longlist} -->
<!-- This is the rest of the second item of the outer list. -->
<!-- \item[3.] -->
<!-- This is the third item of the list. -->
<!-- \end{longlist} -->

<!-- ## Punctuation -->

<!-- Dashes come in three sizes: a hyphen, an intra-word dash like "$U$-statistics" or "the time-homogeneous model"; -->
<!-- a medium dash (also called an "en-dash") for number ranges or between two equal entities like "1--2" or "Cauchy--Schwarz inequality"; -->
<!-- and a punctuation dash (also called an "em-dash") in place of a comma, semicolon, -->
<!-- colon or parentheses---like this. -->

<!-- Generating an ellipsis \ldots\ with the right spacing -->
<!-- around the periods requires a special command. -->

<!-- ## Citation -->

<!-- Simple author and year cite: @billingsley2013convergence. -->
<!-- Multiple bibliography items cite: \cite{billingsley2013convergence,bourbaki1966general} or [@billingsley2013convergence; @bourbaki1966general]. -->
<!-- Author only cite: \citeauthor{ethier1985markov}. -->
<!-- Year only cite: \citeyear{prokhorov1956convergence} or [-@prokhorov1956convergence]. -->

<!-- # Fonts -->

<!-- Please use text fonts in text mode, e.g.: -->
<!-- \begin{itemize} -->
<!-- \item[]\textrm{Roman} -->
<!-- \item[]\textit{Italic} -->
<!-- \item[]\textbf{Bold} -->
<!-- \item[]\textsc{Small Caps} -->
<!-- \item[]\textsf{Sans serif} -->
<!-- \item[]\texttt{Typewriter} -->
<!-- \end{itemize} -->
<!-- Please use mathematical fonts in mathematical mode, e.g.: -->
<!-- \begin{itemize} -->
<!-- \item[] $\mathrm{ABCabc123}$ -->
<!-- \item[] $\mathit{ABCabc123}$ -->
<!-- \item[] $\mathbf{ABCabc123}$ -->
<!-- \item[] $\boldsymbol{ABCabc123\alpha\beta\gamma}$ -->
<!-- \item[] $\mathcal{ABC}$ -->
<!-- \item[] $\mathbb{ABC}$ -->
<!-- \item[] $\mathsf{ABCabc123}$ -->
<!-- \item[] $\mathtt{ABCabc123}$ -->
<!-- \item[] $\mathfrak{ABCabc123}$ -->
<!-- \end{itemize} -->
<!-- Note that \verb|\mathcal, \mathbb| belongs to capital letters-only font typefaces. -->

<!-- # Notes -->

<!-- Footnotes[^1] -->
<!-- pose no problem.[^2] -->

<!-- [^1]: This is an example of a footnote. -->
<!-- [^2]: Note that footnote number is after punctuation. -->

<!-- # Quotations -->

<!-- Text is displayed by indenting it from the left margin. There are short quotations -->

<!-- > This is a short quotation.  It consists of a -->
<!-- > single paragraph of text.  There is no paragraph -->
<!-- > indentation. -->

<!-- and longer ones. -->

<!-- custom blocks syntax https://bookdown.org/yihui/rmarkdown-cookbook/custom-blocks.html -->

<!-- ::: {.quotation data-latex=""} -->
<!-- This is a longer quotation.  It consists of two paragraphs -->
<!-- of text.  The beginning of each paragraph is indicated -->
<!-- by an extra indentation. -->

<!-- This is the second paragraph of the quotation.  It is just -->
<!-- as dull as the first paragraph. -->
<!-- ::: -->

<!-- # Environments -->

<!-- ## Examples for *`plain`-style environments* -->

<!-- ::: {.axiom data-latex=""} -->
<!-- \label{ax1} -->
<!-- This is the body of Axiom \ref{ax1}. -->
<!-- ::: -->

<!-- ::: {.proof data-latex=""} -->
<!-- This is the body of the proof of the axiom above. -->
<!-- ::: -->

<!-- ::: {.claim data-latex=""} -->
<!-- \label{cl1} -->
<!-- This is the body of Claim \ref{cl1}. Claim \ref{cl1} is numbered after -->
<!-- Axiom \ref{ax1} because we used \verb|[axiom]| in \verb|\newtheorem|. -->
<!-- ::: -->

<!-- ::: {.theorem data-latex=""} -->
<!-- \label{th1} -->
<!-- This is the body of Theorem \ref{th1}. Theorem \ref{th1} numbering is -->
<!-- dependent on section because we used \verb|[section]| after \verb|\newtheorem|. -->
<!-- ::: -->

<!-- ::: {.theorem data-latex="[Title of the theorem]"} -->
<!-- \label{th2} -->
<!-- This is the body of Theorem \ref{th2}. Theorem \ref{th2} has additional title. -->
<!-- ::: -->

<!-- ::: {.lemma data-latex=""} -->
<!-- \label{le1} -->
<!-- This is the body of Lemma \ref{le1}. Lemma \ref{le1} is numbered after -->
<!-- Theorem \ref{th2} because we used \verb|[theorem]| in \verb|\newtheorem|. -->
<!-- ::: -->

<!-- ::: {.proof data-latex="[Proof of Lemma \ref{le1}]"} -->
<!-- This is the body of the proof of Lemma \ref{le1}. -->
<!-- ::: -->

<!-- ## Examples for *`remark`*-style environments -->
<!-- ::: {.definition data-latex=""} -->
<!-- \label{de1} -->
<!-- This is the body of Definition \ref{de1}. Definition \ref{de1} is numbered after -->
<!-- Lemma \ref{le1} because we used \verb|[theorem]| in \verb|\newtheorem|. -->
<!-- ::: -->

<!-- ::: {.example data-latex=""} -->
<!-- This is the body of the example. Example is unnumbered because we used \verb|\newtheorem*| -->
<!-- instead of \verb|\newtheorem|. -->
<!-- ::: -->

<!-- ::: {.fact data-latex=""} -->
<!-- This is the body of the fact. Fact is unnumbered because we used \verb|\newtheorem*| -->
<!-- instead of \verb|\newtheorem|. -->
<!-- ::: -->

<!-- # Tables and figures -->
<!-- Cross-references to labeled tables: As you can see in Table\ref{tab:mtc} -->
<!-- and also in Table\ref{parset}. -->
<!-- */% -->

<!-- ```{r mtc, echo = FALSE} -->
<!-- knitr::kable(mtcars, caption = "Table caption", format = "latex", vline = "", linesep = "") -->
<!-- ``` -->

<!-- \begin{table} -->
<!-- \caption{Sample posterior estimates for each model} -->
<!-- \label{parset} -->
<!-- % -->
<!-- \begin{tabular}{@{}lcrcrrr@{}} -->
<!-- \hline -->
<!-- && & &\multicolumn{3}{c}{Quantile} \\ -->
<!-- \cline{5-7} -->
<!-- Model &Parameter & -->
<!-- \multicolumn{1}{c}{Mean} & -->
<!-- Std. dev.& -->
<!-- \multicolumn{1}{c}{2.5\%} & -->
<!-- \multicolumn{1}{c}{50\%}& -->
<!-- \multicolumn{1}{c@{}}{97.5\%} \\ -->
<!-- \hline -->
<!-- {Model 0} & $\beta_0$ & $-$12.29 & 2.29 & $-$18.04 & $-$11.99 & $-$8.56 \\ -->
<!--           & $\beta_1$  & 0.10   & 0.07 & $-$0.05  & 0.10   & 0.26  \\ -->
<!--           & $\beta_2$   & 0.01   & 0.09 & $-$0.22  & 0.02   & 0.16  \\[6pt] -->
<!-- {Model 1} & $\beta_0$   & $-$4.58  & 3.04 & $-$11.00 & $-$4.44  & 1.06  \\ -->
<!--           & $\beta_1$   & 0.79   & 0.21 & 0.38   & 0.78   & 1.20  \\ -->
<!--           & $\beta_2$   & $-$0.28  & 0.10 & $-$0.48  & $-$0.28  & $-$0.07 \\[6pt] -->
<!-- {Model 2} & $\beta_0$   & $-$11.85 & 2.24 & $-$17.34 & $-$11.60 & $-$7.85 \\ -->
<!--           & $\beta_1$   & 0.73   & 0.21 & 0.32   & 0.73   & 1.16  \\ -->
<!--           & $\beta_2$   & $-$0.60  & 0.14 & $-$0.88  & $-$0.60  & $-$0.34 \\ -->
<!--           & $\beta_3$   & 0.22   & 0.17 & $-$0.10  & 0.22   & 0.55  \\ -->
<!-- \hline -->
<!-- \end{tabular} -->
<!-- % -->
<!-- \end{table} -->


<!-- ```{r,echo=FALSE,fig.cap="Figure caption\\label{penG}"} -->
<!-- plot(1:10) -->
<!-- ``` -->

<!-- Sample of cross-reference to figure. -->
<!-- Figure\ref{penG} shows that it is not easy to get something on paper. -->

<!-- # Equations and the like -->

<!-- Two equations: -->
<!-- \begin{equation} -->
<!--     C_{s}  =  K_{M} \frac{\mu/\mu_{x}}{1-\mu/\mu_{x}} \label{ccs} -->
<!-- \end{equation} -->
<!-- and -->
<!-- \begin{equation} -->
<!--     G = \frac{P_{\mathrm{opt}} - P_{\mathrm{ref}}}{P_{\mathrm{ref}}}  100(\%). -->
<!-- \end{equation} -->

<!-- Equation arrays: -->
<!-- \begin{eqnarray} -->
<!--   \frac{dS}{dt} & = & - \sigma X + s_{F} F,\\ -->
<!--   \frac{dX}{dt} & = &   \mu    X,\\ -->
<!--   \frac{dP}{dt} & = &   \pi    X - k_{h} P,\\ -->
<!--   \frac{dV}{dt} & = &   F. -->
<!-- \end{eqnarray} -->
<!-- One long equation: -->
<!-- \begin{eqnarray} -->
<!--  \mu_{\text{normal}} & = & \mu_{x} \frac{C_{s}}{K_{x}C_{x}+C_{s}}  \nonumber\\ -->
<!--                      & = & \mu_{\text{normal}} - Y_{x/s}\bigl(1-H(C_{s})\bigr)(m_{s}+\pi /Y_{p/s})\\ -->
<!--                      & = & \mu_{\text{normal}}/Y_{x/s}+ H(C_{s}) (m_{s}+ \pi /Y_{p/s}).\nonumber -->
<!-- \end{eqnarray} -->

<!-- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
<!-- %% Example with single Appendix:            %% -->
<!-- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->

<!-- ::: {.appendix data-latex=""} -->
<!-- # Title {.unnumbered #appn} -->

<!-- Appendices should be provided in \verb|{appendix}| environment, -->
<!-- before Acknowledgements. -->

<!-- If there is only one appendix, -->
<!-- then please refer to it in text as \ldots\ in the \hyperref[appn]{Appendix}. -->
<!-- ::: -->

<!-- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
<!-- %% Example with multiple Appendixes:        %% -->
<!-- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->

<!-- ::: {.appendix data-latex=""} -->
<!-- # Title of the first appendix {#appA} -->
<!-- If there are more than one appendix, then please refer to it -->
<!-- as \ldots\ in Appendix \ref{appA}, Appendix \ref{appB}, etc. -->

<!-- # Title of the second appendix {#appB} -->

<!-- ## First subsection of Appendix \protect\ref{appB} -->
<!-- Use the standard \LaTeX\ commands for headings in \verb|{appendix}|. -->
<!-- Headings and other objects will be numbered automatically. -->

<!-- \begin{equation} -->
<!-- \mathcal{P}=(j_{k,1},j_{k,2},\dots,j_{k,m(k)}). \label{path} -->
<!-- \end{equation} -->

<!-- Sample of cross-reference to the formula (\ref{path}) in Appendix \ref{appB}. -->
<!-- ::: -->

<!-- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
<!-- %% Support information (funding), if any,   %% -->
<!-- %% should be provided in the                %% -->
<!-- %% Acknowledgements section.                %% -->
<!-- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->

<!-- ## Acknowledgements {.unnumbered} -->

<!-- The authors would like to thank the anonymous referees, an Associate -->
<!-- Editor and the Editor for their constructive comments that improved the -->
<!-- quality of this paper. -->

<!-- The first author was supported by NSF Grant DMS-??-??????. -->

<!-- The second author was supported in part by NIH Grant ???????????. -->


<!-- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
<!-- %% Supplementary Material, if any, should   %% -->
<!-- %% be provided in {supplement} environment  %% -->
<!-- %% with title and short description.        %% -->
<!-- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->

<!-- \begin{supplement} -->
<!-- \stitle{Title of Supplement A} -->
<!-- \sdescription{Short description of Supplement A.} -->
<!-- \end{supplement} -->
<!-- \begin{supplement} -->
<!-- \stitle{Title of Supplement B} -->
<!-- \sdescription{Short description of Supplement B.} -->
<!-- \end{supplement} -->



<!-- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
<!-- %%                  The Bibliography                       %% -->
<!-- %%                                                         %% -->
<!-- %%  imsart-nameyear.bst  will be used to                   %% -->
<!-- %%  create a .BBL file for submission.                     %% -->
<!-- %%                                                         %% -->
<!-- %%  Note that the displayed Bibliography will not          %% -->
<!-- %%  necessarily be rendered by Latex exactly as specified  %% -->
<!-- %%  in the online Instructions for Authors.                %% -->
<!-- %%                                                         %% -->
<!-- %%  MR numbers will be added by VTeX.                      %% -->
<!-- %%                                                         %% -->
<!-- %%  Use \cite{...} to cite references in text.             %% -->
<!-- %%                                                         %% -->
<!-- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
